Preprocess

### 2024-03-18 src/preprocess.Rmd
Final gpt3/4 results from andy - sorted icd as pred - worse perf than first

            "../tmp/healsl_rd1_rapid_gpt3_v2b_first.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt3_v2b_first.csv",

@@

            "../tmp/healsl_rd1_rapid_gpt4_v2b_first.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt4_v2b_first.csv",

>>>>

            "../tmp/healsl_rd1_rapid_gpt3_v2b_sorted.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt3_v2b_sorted.csv",

@@

            "../tmp/healsl_rd1_rapid_gpt4_v2b_sorted.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt4_v2b_sorted.csv",
